Patients with Left Hemispheric Intracerebral Hemorrhage are Less Likely to Receive Neurosurgical Intervention

### 2024-07-08 manuscripts/manuscript1.qmd
figures

library(targets)
library(tidyverse)
library(withr)
library(here)
library(formattable)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)
library(flextable)

# plot stuff
theme_ich <- function(base_family = "Figtree",
                      base_size = 14) {
  theme_minimal(base_size = base_size) +
    theme(
      text = element_text(lineheight = 2),
      plot.title = element_text(size = rel(1.3), margin = margin(12, 0, 8, 0)),
      plot.subtitle = element_text(size = rel(1.1), margin = margin(4, 0, 0, 0)),
      axis.text.y = element_text(size = rel(0.8)),
      axis.title.y = element_text(size = 12, margin = margin(0, 4, 0, 0)),
      axis.text.x = element_text(size = rel(2)),
      axis.title.x = element_blank(),
      legend.position = "bottom",
      legend.justification = 1,
      panel.grid = element_line(colour = "#F3F4F5"),
      plot.caption = element_text(size = rel(0.8), margin = margin(8, 0, 0, 0)),
      plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm")
    )
}

@@

models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neurosurgery_canonical)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_evd_canonical)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_trach_canonical)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_vent_canonical)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_comfort_canonical)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_early_comfort_canonical)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_dnr_canonical))
)

@@

tibble_2 <- bind_cols(column_names, tibble_2) |>
  rename(
    "Right Hemisphere" = "**Right**, N = 1,757",
    "Left Hemisphere" = "**Left**, N = 1,720",
    "Outcome" = ...1
  ) |>
  full_join(table_almost_2, by = "Outcome")

tt(tibble_2, digits = 4)

>>>>

library(targets)
library(tidyverse)
library(withr)
library(here)
library(formattable)
library(gt)
library(gtsummary)
library(modelsummary)
library(marginaleffects)
library(tidybayes)
library(bayesplot)
library(ggdist)
library(patchwork)
library(tinytable)
library(glue)

# plot stuff
theme_ich <- function(base_family = "Figtree",
                      base_size = 14) {
  theme_minimal(base_size = base_size) +
    theme(
      text = element_text(lineheight = 2),
      plot.title = element_text(size = rel(1.3), margin = margin(12, 0, 8, 0)),
      plot.subtitle = element_text(size = rel(1.1), margin = margin(4, 0, 0, 0)),
      axis.text.y = element_text(size = rel(0.8)),
      axis.title.y = element_text(size = rel(0.5), margin = margin(0, 4, 0, 0)),
      axis.text.x = element_text(size = rel(1)),
      axis.title.x = element_blank(),
      legend.position = "bottom",
      legend.justification = 1,
      panel.grid = element_blank(),
      panel.background = element_blank(),
      plot.caption = element_text(size = rel(0.8), margin = margin(8, 0, 0, 0)),
      plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm")
    )
}

@@

models <- list(
  "Neurosurgical Intervention" = with_dir(here(), tar_read(m_posterior_neutral_neurosurgery)),
  "External Ventricular Drain" = with_dir(here(), tar_read(m_posterior_neutral_evd)),
  "Tracheostomy" = with_dir(here(), tar_read(m_posterior_neutral_tracheostomy)),
  "Days of Mechanical Ventilation" = with_dir(here(), tar_read(m_posterior_neutral_days_mechanical_ventilation)),
  "Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_neutral_comfort)),
  "Early Withdrawal of Life-Sustaining Therapy" = with_dir(here(), tar_read(m_posterior_neutral_early_wlst)),
  "DNR Order" = with_dir(here(), tar_read(m_posterior_neutral_dnr_binary))
)

@@

tibble_2 <- bind_cols(column_names, tibble_2) |>
  rename(
    "Right Hemisphere" = "**Right**, N = 1,757",
    "Left Hemisphere" = "**Left**, N = 1,720",
    "Outcome" = ...1
  ) |>
  full_join(table_almost_2, by = "Outcome") |>
  gt()

tibble_2 |>
  fmt_number(columns = 6:7, decimals = 2)

```{r figure 1}
#| echo: false
#| label: figure 1
#| fig-width: 10

predictions(models$"Neurosurgical Intervention", by = "ich_laterality") |>
  posterior_draws() |>
  ggplot(aes(x = draw, fill = ich_laterality)) +
  geom_density(alpha = .7) +
  scale_fill_manual(values = c("#054224", "#ff8800")) +
  scale_y_continuous(
    limits = c(0,100)
  ) +
  scale_x_continuous(
    limits = c(0, 0.14),
    breaks = seq(0, 0.14, 0.02),
    labels = scales::percent
  ) +
  labs(
    title = "Predicted Probability",
    fill = "ICH Laterality",
    y = NULL
  ) +
  theme_ich()

```{r figure 2}
#| echo: false
#| label: figure 2
#| fig-width: 10

predictions(models$"Neurosurgical Intervention", by = c("ich_laterality", "ich_location")) |>
  posterior_draws() |>
  ggplot(aes(x = draw, fill = ich_laterality)) +
  geom_density(alpha = .7) +
  facet_grid(~ich_location) +
  scale_fill_manual(values = c("#054224", "#ff8800")) +
  scale_y_continuous() +
  scale_x_continuous(
    limits = c(0, 0.2),
    breaks = seq(0, 0.20, 0.05),
    labels = scales::percent
  ) +
  labs(
    fill = "ICH Laterality",
    y = NULL
  ) +
  theme_ich()

### 2024-07-08 manuscripts/manuscript1_supplement.qmd
figures

# plot stuff
theme_ich <- function(base_family = "Figtree",
                      base_size = 14) {
  theme_minimal(base_size = base_size) +
    theme(
      text = element_text(lineheight = 2),
      plot.title = element_text(size = rel(1.3), margin = margin(12, 0, 8, 0)),
      plot.subtitle = element_text(size = rel(1.1), margin = margin(4, 0, 0, 0)),
      axis.text.y = element_text(size = rel(0.8)),
      axis.title.y = element_text(size = 12, margin = margin(0, 4, 0, 0)),
      axis.text.x = element_text(size = rel(2)),
      axis.title.x = element_blank(),
      legend.position = "bottom",
      legend.justification = 1,
      panel.grid = element_line(colour = "#F3F4F5"),
      plot.caption = element_text(size = rel(0.8), margin = margin(8, 0, 0, 0)),
      plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm")
    )
}

@@

results_visual <- function(model, title) {
  model <- model
  subtitle <- title

@@

  p2 <- avg_comparisons(model, variables = "ich_laterality") |>
    posterior_draws() |>
    ggplot(aes(x = draw)) +
    geom_density(color = "#054224", fill = "#ff8800") +
    scale_x_continuous(labels = scales::percent) +
    labs(
      title = "Average Difference between Left vs. Right Hemisphere",
      y = NULL
    ) +
    geom_vline(
      xintercept = 0, linetype = "dashed",
      color = "#999999", linewidth = 1
    ) +
    theme_ich()

  p3 <- model |>
    spread_draws(b_ich_lateralityRight) |>
    mutate(ich_right_or = exp(b_ich_lateralityRight)) |>
    ggplot(aes(ich_right_or)) +
    geom_density(color = "#054224", fill = "#ff8800") +
    # stat_halfeye(aes(fill_ramp = stat(x > 1), fill = "#E69F00", color = "#422f05")) +
    scale_x_continuous(breaks = seq(0, 3, 0.25)) +
    labs(
      title = "Odds Ratio - Right Hemisphere",
      y = NULL,
      fill = NULL
    ) +
    geom_vline(
      xintercept = 1, linetype = "dashed",
      color = "#999999", linewidth = 1
    ) +
    theme_ich() +
    theme(legend.position = "none")

  total <- p1 / p2 / p3

  final <- total +
    plot_annotation(
      title = glue(subtitle),
      theme = theme(plot.title = element_text(size = rel(2), margin = margin(12, 0, 8, 0)))
    )

  return(final)
}

@@

```{r prior predictive check - neurosurgery}
#| echo: false
#| warning: false
#| fig-height: 12

@@

@@

@@

@@

###

>>>>

# plot stuff
theme_ich <- function(base_family = "Figtree",
                      base_size = 10) {
  theme_minimal(base_size = base_size) +
    theme(
      text = element_text(lineheight = 2),
      plot.title = element_text(size = rel(1.3), margin = margin(12, 0, 8, 0)),
      plot.subtitle = element_text(size = rel(1.1), margin = margin(4, 0, 0, 0)),
      axis.text.y = element_text(size = rel(0.8)),
      axis.title.y = element_text(size = 12, margin = margin(0, 4, 0, 0)),
      axis.text.x = element_text(size = rel(2)),
      axis.title.x = element_blank(),
      legend.position = "bottom",
      legend.justification = 1,
      panel.grid = element_line(colour = "#F3F4F5"),
      plot.caption = element_text(size = rel(0.8), margin = margin(8, 0, 0, 0)),
      plot.margin = margin(0.25, 0.25, 0.25, 0.25, "cm")
    )
}

@@

results_visual <- function(model) {
  model <- model

@@

  return(p1)
}

@@

```{r prior predictive check - neurosurgery}
#| echo: false
#| warning: false

@@

results_visual(neutral_model)

@@

```{r posterior diagnostics setup}
#| echo: false

posterior_diagnostics <- function(mod) {
  # plot code modified from Andrew Heiss (https://bayesf22-notebook.classes.andrewheiss.com/bayes-rules/13-chapter.html#simulating-the-posterior)

  trace_plot <- mod |>
    gather_draws(`^b_.*`, regex = TRUE) |>
    ggplot(aes(x = .iteration, y = .value, color = factor(.chain))) +
    geom_line(linewidth = 0.1) +
    scale_color_viridis_d(option = "rocket", end = 0.85) +
    facet_wrap(vars(.variable), scales = "free_y")

  trank_plot <- mod |>
    gather_draws(`^b_.*`, regex = TRUE) |>
    group_by(.variable) |>
    mutate(draw_rank = rank(.value)) |>
    ggplot(aes(x = draw_rank, color = factor(.chain))) +
    stat_bin(geom = "step", binwidth = 250, position = position_identity(), boundary = 0) +
    scale_color_viridis_d(option = "rocket", end = 0.85) +
    facet_wrap(vars(.variable), scales = "free_y") +
    theme(axis.text.y = element_blank(), axis.title.y = element_blank(), axis.ticks.y = element_blank())

  # pp_check <- pp_check(mod, ndraws = 500)
  # pp_check_bars <- pp_check(mod, ndraws = 500, type = "bars_grouped", group = "ich_laterality")

  return((trank_plot / trace_plot))
}

@@

```{r posterior diagnostics neurosurgery}
#| echo: false
#| fig-height: 10

posterior_diagnostics(with_dir(here(), tar_read(m_posterior_neutral_neurosurgery)))

```{r posterior diagnostics evd}
#| echo: false
#| fig-height: 10

posterior_diagnostics(with_dir(here(), tar_read(m_posterior_neutral_evd)))

```{r posterior diagnostics trach}
#| echo: false
#| fig-height: 10

posterior_diagnostics(with_dir(here(), tar_read(m_posterior_neutral_tracheostomy)))

```{r posterior diagnostics vent}
#| echo: false
#| fig-height: 10

posterior_diagnostics(with_dir(here(), tar_read(m_posterior_neutral_days_mechanical_ventilation)))

```{r posterior diagnostics comfort}
#| echo: false
#| fig-height: 10

posterior_diagnostics(with_dir(here(), tar_read(m_posterior_neutral_comfort)))

```{r posterior diagnostics early wlst}
#| echo: false
#| fig-height: 10

posterior_diagnostics(with_dir(here(), tar_read(m_posterior_neutral_early_wlst)))

```{r posterior diagnostics dnr}
#| echo: false
#| fig-height: 10

posterior_diagnostics(with_dir(here(), tar_read(m_posterior_neutral_dnr_binary)))

@@

```{r posterior prediction function}
#| echo: false

post_pred <- function(mod) {
  pp_check <- pp_check(mod, ndraws = 500)

  pp_check_bars <- pp_check(mod, ndraws = 500, type = "bars_grouped", group = "ich_laterality")

  return(pp_check / pp_check_bars)
}

### Neurosurgical Intervention

```{r posterior predictions neurosurgery}
#| echo: false

post_pred(with_dir(here(), tar_read(m_posterior_neutral_neurosurgery)))

### Ventriculostomy

```{r posterior predictions evd}
#| echo: false

post_pred(with_dir(here(), tar_read(m_posterior_neutral_evd)))

### Tracheostomy

```{r posterior predictions trach}
#| echo: false

post_pred(with_dir(here(), tar_read(m_posterior_neutral_tracheostomy)))

### Days of Mechanical Ventilation

```{r posterior predictions vent}
#| echo: false

post_pred(with_dir(here(), tar_read(m_posterior_neutral_days_mechanical_ventilation)))

### Comfort Care

```{r posterior predictions comfort}
#| echo: false

post_pred(with_dir(here(), tar_read(m_posterior_neutral_comfort)))

### Early WLST

```{r posterior predictions early wlst}
#| echo: false

post_pred(with_dir(here(), tar_read(m_posterior_neutral_early_wlst)))

### DNR

```{r posterior predictions dnr}
#| echo: false

post_pred(with_dir(here(), tar_read(m_posterior_neutral_dnr_binary)))
